---
title: "Developing Data Products Course: Project 1"
author: "Sergio Contador Pachón"
date: "2 de marzo de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spanish football stadiums

In this project, we see a web page using R Markdown that features a map created with Leaflet.  
The map have markers pointing to each of the football stadiums of the 20 teams 
that participate in 2016-2017 Santander football League of Spain.

The shinny App Web <http://rmarkdown.rstudio.com>.


### R Markdown and Leaflet
here are the steps followed to create the Map:  

#### Load Packages
```{r}
library(leaflet)
```

#### Load Data
```{r}
dir.principal <- paste(getwd(), "/Data", sep = "")

dir <- paste(dir.principal, "/Soccer_Stadium.csv", sep = "")
data <- read.csv(dir)

dir <- paste(dir.principal, "/Icons", sep = "")
dir <- paste(dir, "/", list.files(dir), sep = "")
icons <-  makeIcon( iconUrl = dir, 
                    iconWidth = 31*215/230, 
                    iconHeight = 31,
                    iconAnchorX = 31*215/230/2, 
                    iconAnchorY = 16)

head(data)
```

#### Plot Leaflet Map 
```{r}
addMarkers(addTiles(leaflet()), 
           icon = icons, 
           popup = as.character(data$Stadium), 
           lat = as.numeric(data$Latitude), 
           lng = as.numeric(data$Longitude))
```

